``FISTA'' in Banach spaces with adaptive discretisations

### 2022-03-10 paper.tex
added local-Lipschitz comment

	\begin{theorem}\label{thm: generic a_U and a_E}
		Suppose $\F H= L^2(\Domain)$ for some connected, bounded domain $\Domain\subset\R^d$\edit{ with sufficiently smooth boundary}{} and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$. \edit{If}{For $p\geq0$ and $\meshsize\in(0,1)$, if} $(\tilde{\F{U}}^k)_{k\in\F N}$ is an $\meshsize$-refining sequence of finite element spaces of order $p$, then \edit{}{$(\tilde{\var2}_k)_{k\in\F N}$ is an \aUaE\ for}
		\begin{align*}
			\aU &\leq \splitln{1}{\text{if }q\geq 2,}{\sqrt{\meshsize^{-d}}}{q<2 \edit{}{\text{ and }\sup_{\var0\in\tilde{\F{U}}^0}\frac{\norm{\var0}_{L^\infty(\domain_0)}}{\norm{\var0}_{L^2(\domain_0)}}<\infty},}
			& \aE &\geq \begin{cases}
				\meshsize^{-2p} & \text{if }\op{E} \text{ is $\Norm\cdot$-smooth at }\var0^*,
				\\\meshsize^{-p}\qquad & \text{if }\op{E} \text{ is $\Norm\cdot$-Lipschitz at }\var0^*,
				\\ 1 &\text{otherwise.}
			\end{cases}
		\end{align*}
		\edit{If $\op{g}$ is not Lipschitz at $\var0^*$ but $\op{f}$ is $\Norm\cdot$-Lipschitz and 
		\\$\min_{\var2\in\tilde{\F{U}}^k}\left\{\Norm{\var2-\var0^*}\st \op{g}(\var2)\leq \op{g}(\var0^*)\right\} \lesssim \min_{\var2\in\tilde{\F{U}}^k}\Norm{\var2-\var0^*},$\\
		then, again, $\aE\geq\meshsize^{-p}$.}{}
	\end{theorem}
	The proof of this theorem is in Appendix~\ref{app: generic a_U and a_E}. \edit{}{Note that $\sup_{\var0\in\tilde{\F{U}}^0}\norm{\var0}_{L^\infty(\domain_0)}\norm{\var0}_{L^2(\domain_0)}^{-1}$ is finite whenever $\tilde{\F{U}}^0\subset L^\infty(\Domain)$ is finite dimensional, so this is not a very strong assumption.} The main take-home for this theorem is that the computation of $\aU$ and $\aE$ is typically very simple and clear given a particular choice of $\Norm\cdot$ and $\op{E}$. \edit{The only non-trivial case is when $\op{g}$ is not smooth enough to estimate directly. So long as $\tilde{\F{U}}^k$ are sufficiently dense in sublevel sets of $\op{g}$, the smoothness of $\op{f}$ is sufficient to give a convergence rate.}{}

@@

	\begin{lemma}\label{app:thm: generic a_E bound}
		\edit[2]{Let $(\tilde{\F{U}}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces of order $p$ with $\tilde{\var2}_k=\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)$.}{Suppose $\F H$ and $(\tilde{\F U}^k)_{k\in\F N}$ satisfy Definition~\ref{def: finite element space} and $\var0^*$ is the minimiser of $E$ such that $\Norm{\tilde{\var2}_k-\var0^*}\lesssim \meshsize^{kp}$.}
		\begin{enumerate}
			\item If $\op{E}$ is $\Norm\cdot$-Lipschitz at $\var0^*$, then
			$\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*) \lesssim \meshsize^{kp}\edit[2]{\Norm{\var0^*}}{}$ \edit{}{ (i.e. $p'=p$)}.
			\item If $\op{E}$ is $\Norm\cdot$-smooth at $\var0^*$, then 
			$\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*) \lesssim \meshsize^{2kp}\edit[2]{\Norm{\var0^*}}{}$ \edit{}{ (i.e. $p'=2p$)}.
			\edit[2]{\item If $\op{f}$ is $\Norm\cdot$-Lipschitz at $\var0^*$ and 
			$$\min_{\var2\in\tilde{\F{U}}^k}\left\{\Norm{\var2-\var0^*}\st \op{g}(\var2)\leq \op{g}(\var0^*)\right\} \lesssim \min_{\var2\in\tilde{\F{U}}^k}\Norm{\var2-\var0^*}$$
			uniformly for $k\in\F N$, then
			$\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*) \lesssim \meshsize^p\Norm{\var0^*}.$}{}
		\end{enumerate}
	\end{lemma}
	\begin{proof}
		\edit[2]{Each statement is}{Both statements are direct} by definition, observe
		\begin{gather}
			\op{E}(\edit[2]{\var2}{\tilde{\var2}_k})-\op{E}(\var0^*) \leq \op{Lip}(\op{E})\Norm{\edit[2]{\var2}{\tilde{\var2}_k}-\var0^*},
			\\\op{E}(\edit[2]{\var2}{\tilde{\var2}_k})-\op{E}(\var0^*) \leq \IP{\nabla\op{E}(\var2)}{\edit[2]{\var2}{\tilde{\var2}_k}-\var0^*} = \IP{\nabla \op{E}(\edit[2]{\var2}{\tilde{\var2}_k})-\nabla \op{E}(\var0^*)}{ \edit[2]{\var2}{\tilde{\var2}_k}-\var0^*} \leq \op{Lip}(\nabla\op{E})\Norm{\edit[2]{\var2}{\tilde{\var2}_k}-\var0^*}^2\edit[2]{,
			\\\op{E}(\edit[2]{\var2}{\tilde{\var2}_k})-\op{E}(\var0^*) \leq \op{f}(\edit[2]{\var2}{\tilde{\var2}_k})-\op{f}(\var0^*) \leq \op{Lip}(\op{f})\Norm{\edit[2]{\var2}{\tilde{\var2}_k}-\var0^*}}{}.
		\end{gather}
		\edit[2]{Minimising over the right-hand side over $\var2$ and substituting the definition of order gives the desired result.}{The proof is concluded by using the approximation bounds of $\tilde{\var2}_k$ in Definition~\ref{def: finite element space}.}
		\qed\end{proof}

>>>>

	\begin{theorem}\label{thm: generic a_U and a_E}
		Suppose $\F H= L^2(\Domain)$ for some connected, bounded domain $\Domain\subset\R^d$\edit{ with sufficiently smooth boundary}{} and $\norm\cdot_q\lesssim \Norm\cdot$ for some $q\in[1,\infty]$. \edit{If}{For $p\geq0$ and $\meshsize\in(0,1)$, if} $(\tilde{\F{U}}^k)_{k\in\F N}$ is an $\meshsize$-refining sequence of finite element spaces of order $p$, then \edit{}{$(\tilde{\var2}_k)_{k\in\F N}$ is an \aUaE\ for}
		\begin{align*}
			\aU &\leq \splitln{1}{\text{if }q\geq 2,}{\sqrt{\meshsize^{-d}}}{q<2 \edit{}{\text{ and }\sup_{\var0\in\tilde{\F{U}}^0}\frac{\norm{\var0}_{L^\infty(\domain_0)}}{\norm{\var0}_{L^2(\domain_0)}}<\infty},}
			& \aE &\geq \begin{cases}
				\meshsize^{-2p} & \text{if }\nabla\op{E} \text{ is $\Norm\cdot$-Lipschitz at }\var0^*,
				\\\meshsize^{-p}\qquad & \text{if }\op{E} \text{ is $\Norm\cdot$-Lipschitz at }\var0^*,
				\\ 1 &\text{otherwise.}
			\end{cases}
		\end{align*}
		\edit{If $\op{g}$ is not Lipschitz at $\var0^*$ but $\op{f}$ is $\Norm\cdot$-Lipschitz and 
		\\$\min_{\var2\in\tilde{\F{U}}^k}\left\{\Norm{\var2-\var0^*}\st \op{g}(\var2)\leq \op{g}(\var0^*)\right\} \lesssim \min_{\var2\in\tilde{\F{U}}^k}\Norm{\var2-\var0^*},$\\
		then, again, $\aE\geq\meshsize^{-p}$.}{}
	\end{theorem}
	The proof of this theorem is in Appendix~\ref{app: generic a_U and a_E}. \edit{}{Note that $\sup_{\var0\in\tilde{\F{U}}^0}\norm{\var0}_{L^\infty(\domain_0)}\norm{\var0}_{L^2(\domain_0)}^{-1}$ is finite whenever $\tilde{\F{U}}^0\subset L^\infty(\Domain)$ is finite dimensional, so this is not a very strong assumption.} The main take-home for this theorem is that the computation of $\aU$ and $\aE$ is typically very simple and clear given a particular choice of $\Norm\cdot$ and $\op{E}$. \edit{The only non-trivial case is when $\op{g}$ is not smooth enough to estimate directly. So long as $\tilde{\F{U}}^k$ are sufficiently dense in sublevel sets of $\op{g}$, the smoothness of $\op{f}$ is sufficient to give a convergence rate.}{We also briefly remark that the Lipschitz constants in this lemma do not need to be valid globally, only on the sequence $\tilde{\var2}_k$. The same result holds under a local-Lipschitz assumption, for example on the ball of radius $\sup_{k\in\F N}\Norm{\tilde{\var2}_k}$ which is finite whenever $p\geq0$.}

@@

	\begin{lemma}\label{app:thm: generic a_E bound}
		\edit[2]{Let $(\tilde{\F{U}}^k)_k$ be a sequence of $\meshsize$-refining finite element spaces of order $p$ with $\tilde{\var2}_k=\argmin_{\var0\in\tilde{\F{U}}^k}\op{E}(\var0)$.}{Suppose $\F H$ and $(\tilde{\F U}^k)_{k\in\F N}$ satisfy Definition~\ref{def: finite element space} and $\var0^*$ is the minimiser of $E$ such that $\Norm{\tilde{\var2}_k-\var0^*}\lesssim \meshsize^{kp}$.}
		\begin{enumerate}
			\item If $\op{E}$ is $\Norm\cdot$-Lipschitz at $\var0^*$, then
			$\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*) \lesssim \meshsize^{kp}\edit[2]{\Norm{\var0^*}}{}$ \edit{}{ (i.e. $p'=p$)}.
			\item If $\nabla\op{E}$ is $\Norm\cdot$-Lipschitz at $\var0^*$, then 
			$\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*) \lesssim \meshsize^{2kp}\edit[2]{\Norm{\var0^*}}{}$ \edit{}{ (i.e. $p'=2p$)}.
			\edit[2]{\item If $\op{f}$ is $\Norm\cdot$-Lipschitz at $\var0^*$ and 
			$$\min_{\var2\in\tilde{\F{U}}^k}\left\{\Norm{\var2-\var0^*}\st \op{g}(\var2)\leq \op{g}(\var0^*)\right\} \lesssim \min_{\var2\in\tilde{\F{U}}^k}\Norm{\var2-\var0^*}$$
			uniformly for $k\in\F N$, then
			$\op{E}(\tilde{\var2}_k)-\op{E}(\var0^*) \lesssim \meshsize^p\Norm{\var0^*}.$}{}
		\end{enumerate}
	\end{lemma}
	\begin{proof}
		\edit[2]{Each statement is}{Both statements are direct} by definition, observe
		\begin{gather}
			\op{E}(\edit[2]{\var2}{\tilde{\var2}_k})-\op{E}(\var0^*) \leq \op{Lip}(\op{E})\Norm{\edit[2]{\var2}{\tilde{\var2}_k}-\var0^*},
			\\\op{E}(\edit[2]{\var2}{\tilde{\var2}_k})-\op{E}(\var0^*) \leq \IP{\nabla\op{E}(\var2)}{\edit[2]{\var2}{\tilde{\var2}_k}-\var0^*} = \IP{\nabla \op{E}(\edit[2]{\var2}{\tilde{\var2}_k})-\nabla \op{E}(\var0^*)}{ \edit[2]{\var2}{\tilde{\var2}_k}-\var0^*} \leq \op{Lip}(\nabla\op{E})\Norm{\edit[2]{\var2}{\tilde{\var2}_k}-\var0^*}^2\edit[2]{,
			\\\op{E}(\edit[2]{\var2}{\tilde{\var2}_k})-\op{E}(\var0^*) \leq \op{f}(\edit[2]{\var2}{\tilde{\var2}_k})-\op{f}(\var0^*) \leq \op{Lip}(\op{f})\Norm{\edit[2]{\var2}{\tilde{\var2}_k}-\var0^*}}{}.
		\end{gather}
		\edit[2]{Minimising over the right-hand side over $\var2$ and substituting the definition of order gives the desired result.}{The proof is concluded by using the approximation bounds of $\tilde{\var2}_k$ in Definition~\ref{def: finite element space}.}
	\qed\end{proof}
